Application-Level Regression Testing Framework using Jenkins

### 2017-03-22 manuscript/manuscript.tex
added to pwauth, https otp section

/etc/sysconfig/iptables:
-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
-p tcp --dport 22 -j ACCEPT
-A INPUT -s 172.16.0.0/15 -m state --state NEW -m tcp 
-p tcp --dport 22 -j ACCEPT *delete maybe*
-A INPUT  -m state --state NEW -m tcp -p tcp --dport 80 
-j ACCEPT
-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
-p tcp --dport 443 -j ACCEPT

@@

 /usr/local/bin/pwauth+session: 
 https://github.com/reubendb/BasicAuthOTPSession
 /blob/master/BasicAuthOTPSession.py#L1
\end{lstlisting}
\subsection{LDAP with Jenkins}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
\\
My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

>>>>

/etc/sysconfig/iptables:
-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
-p tcp --dport 22 -j ACCEPT
-A INPUT -s 172.16.0.0/15 -m state --state NEW -m tcp 
-p tcp --dport 22 -j ACCEPT 
-A INPUT  -m state --state NEW -m tcp -p tcp --dport 80 
-j ACCEPT
-A INPUT -s 141.142.0.0/16 -m state --state NEW -m tcp 
-p tcp --dport 443 -j ACCEPT

@@

 NOTE: Install  mod_authnz_external native package

  /etc/pam.d/pwauth:
 #%PAM-1.0
 auth	   required	/lib64/security/pam_securid.so
 account    include      password-auth

 /usr/local/bin/pwauth+session: 
 https://github.com/reubendb/BasicAuthOTPSession
 /blob/master/BasicAuthOTPSession.py#L1

\end{lstlisting}
\subsection{LDAP with Jenkins}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
\\
My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore
